---
title: "Project 3 - Breast Cancer Analysis and Zillow Analysis"
output: html_notebook
---

Part B

Import data from UCI machine learning library
```{r}
uciwd ="https://archive.ics.uci.edu/ml/machine-learning-databases/"
mldata = paste(uciwd,"breast-cancer-wisconsin/breast-cancer-wisconsin.data", sep="")
bcancer = read.csv(mldata)   # Treat the first row as variable names
bcancer
bcancer = read.csv(mldata, header=F) # Treat the data begins from the first row

colnames(bcancer)=c("ID","clump_thick","cell_size","cell_shape", "marginal","epithelial","nuclei",
                    "chromatin","nucleoli","mitoses","class")
```
View and analyze data
```{r}
str(bcancer)
summary(bcancer)
table(bcancer$nuclei)
```
Manipulate the data
```{r}
bcancer$nuclei = as.numeric(gsub("\\?","NA",bcancer$nuclei))
library(DMwR)
bcancer = knnImputation(bcancer)
bcancer$class=factor(bcancer$class)
```
Run logistic function and find variables with significance to predict
```{r}
bcancer_logit = glm(class~., data=bcancer, family="binomial")
summary(bcancer_logit)
```

Part C

Source data from original script. Remove variables with too many missing values. 
```{r}
source("D03c_zillow.R", echo = TRUE)

good_features = filter(missing_values, missing_pct<0.25)
good_features

gfeature = as.vector(good_features[,1])

```
Subsetting needed variables from the big dataset.
```{r}
zdata.a = subset(cor_tmp, select=c('logerror', gfeature))
zdata3 = subset(cor_tmp, select=c('abs_logerror', gfeature))
```
Removing geographical and other variables not needed.
```{r}
# abs_logerror
zdata4 = subset(zdata3, select = -c(2,8,10,11,13,14,15,16,17,19,22,23,24,25,28))
# logerror
zdata.log = subset(zdata.a, select = -c(2,8,10,11,13,14,15,16,17,19,22,23,24,25,28))
```
Correlation plot 
```{r}
corrplot(cor(zdata4, use = "complete.obs"), type = "lower", method = 'number')
```
Removing highly correlated variables for loerror and abs_logerror dataset.
```{r}
# abs_logerror
zdata4_1 = subset(zdata4, select = -c(num_bathroom_calc, num_bath, area_total_calc))
# logerror
zdata.log_1 = subset(zdata.log, select = -c(num_bathroom_calc, num_bath, area_total_calc))
```
Convert variables to numeric before running linear regression.
```{r}
# abs_logerror
zdata4_1$area_live_finished = as.numeric(zdata4_1$area_live_finished)
zdata4_1$region_county = as.numeric(zdata4_1$region_county)
# logerror
zdata.log_1$area_live_finished = as.numeric(zdata.log_1$area_live_finished)
zdata.log_1$region_county = as.numeric(zdata.log_1$region_county)
```
Took one last look at the data frame structure before runnnig linear regression.
```{r}
# logerror
str(zdata.log_1)
# abs_logerror
str(zdata4_1)
```
Linear regression and regression subsets for logerror.
```{r}
# logerror
fit.logerror = lm(logerror~.,zdata.log_1)
summary(fit.logerror)
regfit.logerror = regsubsets(logerror~.,zdata.log_1)
summary(regfit.logerror)
```
Linear regression and regression subsets for abs_logerror.
```{r}
# abs_logerror
fit.abs_logerror = lm(abs_logerror~.,zdata4_1)
summary(fit.abs_logerror)
regfit.abs_logerror = regsubsets(abs_logerror~.,zdata4_1)
summary(regfit.abs_logerror)
```

Explanation of results

The absolute value logerror (abs_logerror) model has more predictor variables with a stronger correlation to the dependent variable. The num_room variable didn't have any significance in any of the models and I would suggest to remove it. 


